Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-05-28 article.tex
wording
Add the notion of independance

One way to emphasize the connections between neurons is to represent them by a
(un)directed graph with $p$ nodes: each node represents a neuron, and each
edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
Formally, the challenge problem may be formulated by the following statement :
\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of fluorescent
calcium concentration of size $n$ from $p$ neurons, the goal is to infer the
connectivity network $y \in \left\{0, 1\right\}^{p \times p}$ where
non zero values indicate that the neuron $i$ have an outward connection to
the neuron $j$.}

From a probabilistic point of view, the newtwork

% Plan:
% introduce the notion of dependance/independance
% Introduce correlation => Estimator of I(X; Y)
%                       => Issue indirect effect
% Introduce partial correlation => Estimator of I(X; Y | Z)
%                               => Symmetric measure
% Introduce a custom solution to make the Y matrix assymetric
% Introduce Filtering

>>>>

% Introduce notation + goal in mathematical score
% TODO check convention for y_{ij}
One way to emphasize the connections between neurons is to represent them by a
(un)directed graph with $p$ nodes: each node represents a neuron, and each
edge $y_{ij}$ represents a direct link from neuron  $i$ to neuron $j$. If the
graph is undirected, then $y_{ij}$ is equal to $y_{ji}$  for all $i,j$.
The unsupervised task may be formulated as:
\textit{Given $X \in \mathcal{R}^{n \times p}$  a set of $p$ time series of
fluorescent calcium concentration of size $n$ from $p$ neurons, the goal is to
infer the connectivity graph $y \in \left\{0, 1\right\}^{p \times p}$.}

% introduce the notion of dependance/independance
From a probabilistic point of view, the inference of the undirected network
can be formulated as inferring the conditional independence between neurons
$i$ and $j$ conditionally to all other neurons
$i \perp j | 1,\ldots,p \backslash \left\{i, j\right\}$. Note that
the unconditional independence $i \perp j$ between  $i$ and $j$ doesn't allow to
infer the graph due to indirect effect. For instance if neurons $A, B, C$ have
the connectivity graph $A \rightarrow B \rightarrow C$, then we have the
dependence $A \not\perp C$ and the conditional independence $A \perp C | B$.

% Introduce correlation => Estimator of I(X; Y)
%                       => Issue indirect effect
% Introduce partial correlation => Estimator of I(X; Y | Z)
%                               => Symmetric measure
% Introduce a custom solution to make the Y matrix assymetric
% Introduce Filtering
